Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-03-01 scnn.tex
meeting changes

@@

\title{Efficient spherical Convolutional Neural Networks}

@@

\subsection{Motivation}
a) Cosmology has a lot of spherical data. Our solution is easy to use and is based on the widely used healpix sampling.
b) It is the most efficient spherical convolution

\subsection{Potential applications}
\begin{itemize}
	\item Efficient compression de-compression of 360 videos\cite{su2017learning}
	\item Analysis of spherical cosmological data such as the cosmic microwave background \cite{...}, already done in\cite{he2018analysis}.
\end{itemize}

\subsection{Related work}
\cite{cohen2017convolutional} \nati{+ add other graph CNN approaches \cite{...}}
\cite{cohen2018spherical}
\cite{boomsma2017spherical}
\cite{defferrard2016convolutional}

\section{Spherical convolution on sphere using a graph}
\begin{itemize}
	\item We build a graph using the healpix sampling
	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
\end{itemize}

\section{Efficient spherical CNN}
\begin{itemize}
	\item We need efficient convolution, hence the Chebysheff trick
	\item Define spherical CNN using graph CNN
\end{itemize}

\section{Experiments}
\begin{itemize}
	\item With the entire sphere / different PSD (The PSD features + linear SVM is equivalently good)
	\item Without the entire sphere / same PSD (The histogram features + kernelized SVM is equivalently good)
	\item ??
\end{itemize}

>>>>

\newcommand{\assign}[1]{{\color[rgb]{.8,.5,.8}{Assigned: #1 }}}

@@

\title{Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications}

@@

\subsection{Motivation}
\assign{Tomek}

a) Cosmology has a lot of spherical data. Our solution is easy to use and is based on the widely used healpix sampling.
b) It is the most efficient spherical convolution

\subsection{Potential applications}
	\assign{Tomek, Nathanael}

\begin{itemize}

	\item Efficient compression de-compression of 360 videos\cite{su2017learning}
	\item Analysis of spherical cosmological data such as the cosmic microwave background \cite{...}, already done in\cite{he2018analysis}.
\end{itemize}

\subsection{Related work}
\assign{Nathanael}
\cite{cohen2017convolutional} \nati{+ add other graph CNN approaches \cite{...}}
\cite{cohen2018spherical}
\cite{boomsma2017spherical}
\cite{defferrard2016convolutional}

\section{Spherical convolution on sphere using a graph}
\assign{Nathanael}

\begin{itemize}
	\item We build a graph using the healpix sampling
	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
\end{itemize}

\section{Efficient spherical CNN}
\assign{Michael}

\begin{itemize}
	\item We need efficient convolution, hence the Chebysheff trick
	\item Define spherical CNN using graph CNN
\end{itemize}

\section{Experiments}
\assign{Nathanael, Tomek}

\begin{itemize}
	\item With the entire sphere / different PSD (The PSD features + linear SVM is equivalently good)
	\item Without the entire sphere / same PSD (1 sample: the histogram features + kernelized SVM is equivalently good)
	\item ??
\end{itemize}
